Shapes analysis for time series.

### 2024-05-22 NEURIPS24/paper.tex
update

 All these state-of-the-art methods previously mentionned \cite{glaunes2008large,oh2024stable,wu2024shape,heo2024logistic} are comapred to TS-LDDMM in \Cref{appendix:classification_shape_analysis}.
  \section{Limitations}
  \label{sec:limitations}
  While TS-LDDMM performs well on shape-based datasets, it assumes a certain degree of homogeneity with the existence of a reference time series graph$\msg_0$.
 Extending TS-LDDMM to more heterogeneous datasets using clustering is ongoing work.
 TS-LDDMM employs kernel computations, which require specific libraries (e.g., KeOps \cite{charlier2021kernel}) to be efficient and scalable.
 However, in our experiments, the time complexity of TS-LDDMM is comparable to that of competitors.
 It is clear that TS-LDDMM needs to be extended to handle very large datasets with high-dimensional time series (such as videos).
 Additionally, TS-LDDMM requires tuning several hyperparameters, though this is a common requirement among competitors \cite{glaunes2008large, oh2024stable, wu2024shape, heo2024logistic}.
 In future work, adaptive methods are expected to be developed to provide a more user-friendly interface.
  %\color{red} rappeler les limites de la méthodes : petite dimension à cause des kernels, tuner les hyper paramètres correctement, version adaptative}
\section{Conclusion}
\vspace{-1ex}
This paper proposes a feature representation method, TS-LDDMM, designed for 
shape comparison on homogeneous time series datasets. We show on a real dataset 
its ability to study, with high interpretability, the inter-individual shape 
variability. As an unsupervised approach, it is user-friendly and enables knowledge 
transfer for different supervised tasks such as classification. Although TS-LDDMM 
is already competitive for classification, its performances can be leveraged on 
more heterogeneous datasets using a hierarchical clustering extension, which is relegated for future work.

>>>>

 All these state-of-the-art methods previously mentionned \cite{glaunes2008large,oh2024stable,wu2024shape,heo2024logistic} are compared to TS-LDDMM in \Cref{appendix:classification_shape_analysis}.
  \section{Limitations and conclusion}
  \label{sec:limitations}
  \paragraph*{Limitations}
  While TS-LDDMM performs well on shape-based datasets, it assumes a certain degree of homogeneity with the existence of a reference time series graph$\msg_0$.
 Extending TS-LDDMM to more heterogeneous datasets using clustering is ongoing work.
 TS-LDDMM employs kernel computations, which require specific libraries (e.g., KeOps \cite{charlier2021kernel}) to be efficient and scalable.
 However, in our experiments, the time complexity of TS-LDDMM is comparable to that of competitors.
 It is clear that TS-LDDMM needs to be extended to handle very large datasets with high-dimensional time series (such as videos).
 Additionally, TS-LDDMM requires tuning several hyperparameters, though this is a common requirement among competitors \cite{glaunes2008large, oh2024stable, wu2024shape, heo2024logistic}.
 In future work, adaptive methods are expected to be developed to provide a more user-friendly interface.
  %\color{red} rappeler les limites de la méthodes : petite dimension à cause des kernels, tuner les hyper paramètres correctement, version adaptative}
\paragraph*{Conclusion}
\vspace{-1ex}
This paper proposes a feature representation method, TS-LDDMM, designed for 
shape comparison on homogeneous time series datasets. We show on a real dataset 
its ability to study, with high interpretability, the inter-individual shape 
variability. As an unsupervised approach, it is user-friendly and enables knowledge 
transfer for different supervised tasks such as classification. Although TS-LDDMM 
is already competitive for classification, its performances can be leveraged on 
more heterogeneous datasets using a hierarchical clustering extension, which is relegated for future work.
